SPARQL on the open, decentralised Web

### 2016-06-02 dissertation/related.tex
really do the developer stuff?
ldp in related work

@@

\subsection{Tools for developer efficiency}
\todo{more here}

>>>>

Under the auspices of the  World Wide Web Consortium a standard for
read-write applications using RDF has been developed: The Linked Data
Platform \cite{ldp1}. The abstract in the specification describes it
as:
\begin{quote}
Linked Data Platform (LDP) defines a set of rules for HTTP operations
on web resources, some based on RDF, to provide an architecture for
read-write Linked Data on the web.
\end{quote}
While developers who are familiar with HTTP-based applications and
Linked Data may feel familiar with the platform, it still requires
that they read and understand the specification to be able to use it,
and therefore, it is not hypermedia, and I think it misses out on many
of the benefits of hypermedia. A discussion at the Developers Workshop
at the Extended Semantic Web Conference 2015\footnote{see
  \url{https://www.youtube.com/watch?v=F4WN4XEpViA} for a recording of
  the discussion session.} found rough consensus around a comment
formulated by me:
\begin{quote}
LDP has to be superseded by hypermedia in some way.
\end{quote}

@@

%\subsection{Tools for developer efficiency}
%\todo{more here}
